Market simulator

### 2020-10-16 analysis/05_market_simulator.Rmd
Some commit

organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_reactive <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_name = "organization_config01.csv"
    organization_values$file_type = "csv"
    organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  } else {
    organization_data <- read.csv(input$org_update$datapath)
    organization_values$file_name = input$org_update$name
    organization_values$file_size = input$org_update$size
    organization_values$file_type = input$org_update$type
    organization_values$file_path = input$org_update$datapath
  }
})

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(organization_data()[1:4,][which(organization_data()[1:4,2] == 1), 1]),
    width = "450px"
  )

})

>>>>

organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_name = "organization_config01.csv"
    organization_values$file_type = "csv"
    organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  } else {
    organization_data <- read.csv(input$org_update$datapath)
    organization_values$file_name = input$org_update$name
    organization_values$file_size = input$org_update$size
    organization_values$file_type = input$org_update$type
    organization_values$file_path = input$org_update$datapath
  }
})

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  organization_data = organization_data()

  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
    width = "450px"
  )
})
